Verifying Demonstrations

### 2019-02-27 paper/verifiability-analysis.tex
Requirements aims towards something

\Cref{CountOnce} prevents Sybil attacks, in the sense
that Alice cannot provide two (or more) participation proofs for a
specific protest and thus be counted more than once.
To do this she must create more than one pseudonym, \(\pid\).
Indeed, to be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) such that the verifier\footnote{%
  Here the verifier is either the witness during the distance bounding or the 
  verifier who tries to verify the count.
} accepts the proof
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
As a consequence, this is reduced to the security of the \(\AC\) scheme.
Remember, by assumption the \ac{CA} will issue only one signature for such a 
key, so Alice cannot ask for a second one.

@@

\Cref{DesignatedEvent} is to prevent Alice (or someone else) from reusing the same proof (or proof share) for another event.
This possibility is prevented through the use of \(\cid\) in the proof shares.
To reuse the proof share for another protest, with a different manifesto, one 
must find a second pre-image \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
  \Hash[\mfst']\).

>>>>

\Cref{CountOnce} aims to prevent Sybil attacks, in the sense
that Alice cannot provide two (or more) participation proofs for a
specific protest and thus be counted more than once.
To do this she must create more than one pseudonym, \(\pid\).
Indeed, to be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) such that the verifier\footnote{%
  Here the verifier is either the witness during the distance bounding or the 
  verifier who tries to verify the count.
} accepts the proof
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
As a consequence, this is reduced to the security of the \(\AC\) scheme.
Remember, by assumption the \ac{CA} will issue only one signature for such a 
key, so Alice cannot ask for a second one.

@@

\Cref{DesignatedEvent} aims to prevent Alice (or someone else) from reusing the 
same proof (or proof share) for another event.
This possibility is prevented through the use of \(\cid\) in the proof shares.
To reuse the proof share for another protest, with a different manifesto, one 
must find a second pre-image \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
  \Hash[\mfst']\).
